A community-maintained standard library of population genetic simulations

### 2019-12-17 popSimManu.tex
added text about dmel sims to methods
added text about dmel sims to methods

In Figure \ref{fig:IM_popn_human}C we show estimates of population sizes and divergence
time from each of the methods for samples simulated for the African and European populations
under the \cite{gutenkunst2009inferring} model. Each of the methods compared has stronger
and weaker points to their accuracy across parameters. For instance the simple, IM-style
analyses we have performed do not capture recent population size change in CEU, however
they do a good job of estimating the quite simple YRI population size history.

@@

The broad brush comparisons we have done, while far from exhaustive, are informative,
and highlight the utility of easy comparison of methods on the same footing.
The tests here were under best-case scenarios --
simulations of discrete, randomly mating populations that fit the assumptions of the methods nearly exactly --
and yet different methods, as well as applications of the same method
to different simulations of the same model,
produced somewhat different results.

@@

From HomSap we ran replicate whole genome simulations under the model
and specified taking 20 samples each from the Europe and Africa populations. 
For DroMel, runtimes under OutOfAfrica\_2L06 were prohibitively slow for
running whole genome simulations. Instead we simulated 3 Mb of chromosome 2R.
and take 50 samples from each of
the Africa and Europe populations. We tried to run whole genome simulations under
this model but after XXXX amount of time... (JRA fill in details here). For the generic
IM simulations, we used the HomSap genome along with the HapmapII\_GRCh37 genetic map,
and sampled 20 individuals from each population.

>>>>

In Figure \ref{fig:IM_popn_human}C we show estimates of population sizes and divergence
time from each of the methods for samples simulated for the African and European populations
under the \cite{gutenkunst2009inferring} model. Each of the methods compared has stronger
and weaker points to their accuracy across parameters. For instance the simple, IM-style
analyses we have performed do not capture recent population size change in CEU, however
they do a good job of estimating the more simple simulated YRI population size history.

@@

The broad brush comparisons we have done, while far from exhaustive, are informative,
and highlight the utility of easy comparison of methods on the same footing.
The tests here were under best-case scenarios --
simulations of discrete, randomly mating populations that evolve neutrally and 
fit the assumptions of the methods nearly exactly --
and yet different methods, as well as applications of the same method
to different simulations of the same model,
produced somewhat different results.

@@

From HomSap we ran replicate whole genome simulations under the model
and specified taking 20 samples each from the Europe and Africa populations. 
For DroMel, runtimes under OutOfAfrica\_2L06 were prohibitively slow when simulating whole genomes.
For example, both chromosomes 3R and X failed to coalesce within 30 days of starting using $n = 50$. 
Runtimes using the identical sample size were 19, 21, and 12 days for chromosomes 2L, 2R, and 3L, 
respectively. For this reason, we chose to present only data from chromosome 2R for simulations
under OutOfAfrica\_2L06. For the generic IM simulations, we used the HomSap genome along with the 
HapmapII\_GRCh37 genetic map, and sampled 20 individuals from each population.
